---
title: "Introduction of Exploration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exploration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
knitr::opts_chunk$set(include = FALSE)
library(SSMimpute)
library(tidyverse)
library(knitr)
library(imputeTS)
library(dlm)
library(crayon)
library(MASS)
library(bcp)
library(shrinkTVP)
```
As we mentioned in the Quick start, we usually need an initial guess of formula, and set up the `ss_param` and `cpt_learning_param`, this requires our knowledge of each coefficient $\beta_{j,t}$ and we will ask questions of whether this variables should goes into our model, what is the state-space equation, what is an appropriate initial value and if there is any change point. Sometimes this question can be answered by domain knowledge. Here we provide a function for an automatically exploration and help users identify the formula and parameters as easy as a one line code. The idea is based on `shrinkTVP` which incorporates Bayesian hierarchical shrinkage for state-space model, to achieve a two-way sparsity. Details can be found:..

```{r}
head(data_complex)
res = shrinkTVP(formula = y ~ y_1 + x + x_1 + c, data = data_complex)
```
We start our exploration:
```{r}
explore_SSM(res = res)
```
Based on the figures, we notice coefficient of `x` and `c` are probably non-stationary, we further using `bcp` for a Bayesian change point detection, gives a posterior probability of change point in each change point. We notice a clear change point for `x` is 400 and 700. and the coefficent for `c` is probably a random walk.



